---
author: " "
title: "Homework Assignment 1:Functions and Matrix Algebra in R "
output:
  html_document: default
  pdf_document: default
---
# Question1 
# Question2
# Question3



```{r}

```

# Q1(a) equally weighted portfolio
```{r}
expected_r = matrix(c(0.08,0.0101,0.075,-0.01),nrow=4)
equal_w = matrix(c(1/4,1/4,1/4,1/4),nrow=4)
expected_r = t(equal_w)%*%expected_r

standard_d =matrix(c(0.175,0.212,0.195,0.142),nrow=4)
C =matrix(c(1.000,0.770,0.670,-0.070,0.770,1.000,0.600,-0.110,0.670,
                0.600,1.000,-0.050,-0.070,-0.110,-0.050,1.000),nrow=4,byrow = T)
sig1 = c(0.175,0.212,0.195,0.142)
sig1_transpose = t(sig1)  # t(vector) transposes vector or matrix
sig = sig1 %*% sig1_transpose #sig1 [2x1] and sig1_t [1x2]->[2x2]
V=sig*C

standard_d = sqrt(t(equal_w)%*%V%*%equal_w)
expected_r
standard_d
```

# Q1(b) weight for having maximum sharpe ratio
```{r}
R = matrix(c(0.08,0.0101,0.075,-0.01),nrow=4)
I = matrix(c(1,1,1,1),nrow=4)
A = solve(V) %*% R
A1 = t(I)%*%solve(V)%*%R
w = A%*%solve(A1)
w
```

# Q1(c)  expected return for having maximum sharpe ratio
```{r}
ER = t(w)%*%R
ER
```

# Q1(d)  expected standard deviation for having maximum sharpe ratio
```{r}
SD = matrix(c(0.175,0.212,0.195,0.142),nrow=4)
SD_p =  sqrt(t(w)%*%V%*%w)
SD_p
```


# Q1(e)  SD and ER for having minimum sharpe ratio
```{r}
Wmin1 = solve(V)%*%I
Wmin2 = t(I)%*%solve(V)%*%I
Wmin = Wmin1%*%solve(Wmin2)
ERmin = t(Wmin)%*%R
SDmin = sqrt(t(Wmin)%*%V%*%Wmin)
ERmin
SDmin
```

# Q2 Create a Function for valuing either a delayed perpetuity or a delayed annuity.
```{r}
# The inputs that had been selected were impermissible if in fact you input a value of g > r
Value <- function(N,M,C,g,r){
  P <- NULL
  V <- NULL
  if(g>0){
    P = C/((1+r)^M*(r-g))
    V = C/(((1+r)^M)*(r-g)*(1-((1+g)/(1+r))^N))
  }
  else{
    P = C/((1+r)^M*r)
    V = (1-((1+g)/(1+r))^N)*C/((1+r)^M)*(r-g)
  }
return(list(P,V))
}
```

# Q3 Using the R Function required in problem 2, graph the value 
```{r}
# here we assume that M=5;g=0;N=20;C=100 and r increases from 0.01 to 0.1
value_g0 <- list()
for(i in 1:20){
  r <- c()
  r[i] <- 0.01+(i)*0.005
  M=5;g=0;N=20;C=100
  value_g0[[i]] <- Value(N,M,C,g,r[i])[[2]]
}
value_g0

# here we assume that M=10;g=0;N=20;C=100 and r increases from 0.01 to 0.1
value_g1 <- list()
for(i in 1:20){
  r <- c()
  r[i] <- 0.01+(i)*0.005
  M=10;g=0;N=20;C=100
  value_g1[[i]] <- Value(N,M,C,g,r[i])[[2]]
}
value_g1

rate <- c()
for (i in 1:20) {
  rate[i] <- 0.01+(i)*0.005
}
# here we assume that M=5;g=0;N=20;C=100 and r increases from 0.01 to 0.1
data0 <- data.frame(value = unlist(value_g0),interest_rate = rate)
library(ggplot2)
ggplot(data0, aes(x = interest_rate, y = value)) +
  geom_line()
# here we assume that M=10;g=0;N=20;C=100 and r increases from 0.01 to 0.1
data1 <- data.frame(value = unlist(value_g1),interest_rate = rate)
ggplot(data1, aes(x = interest_rate, y = value)) +
  geom_line()
```


```{r}

```



```{r}

```

