---
author: " "
title: "lasso function"
output:
  html_document: default
  pdf_document: default
---




## prepare for the data(including response Y and variables X)
```{r}
library(MASS)
library(glmnet)
myData = Boston
names(myData)[14] = "Y"
iLog = c(1, 3, 5, 6, 8, 9, 10, 14);
myData[, iLog] = log(myData[, iLog]);
myData[, 2] = myData[, 2] / 10;
myData[, 7] = myData[, 7]^2.5 / 10^4
myData[, 11] = exp(0.4 * myData[, 11]) / 1000;
myData[, 12] = myData[, 12] / 100;
myData[, 13] = sqrt(myData[, 13]);
X = as.matrix(myData[, -14])
y = myData$Y
lam.seq = c(0.30, 0.2, 0.1, 0.05, 0.02, 0.005) 

```

## one step function
```{r}
  one_step_lasso = function(r, x, lam){
    xx = sum(x^2)
    xr = sum(r*x)
    b = (abs(xr) - lam/2)/xx
    b = sign(xr)*ifelse(b>0, b, 0)
    return(b)}

```

## create my lasso function
```{r}
MyLasso <- function(X, y, lam.seq, maxit=50, standardize = TRUE){
  n = length(y)
  p = dim(X)[2]
  nlam = length(lam.seq)
  B = matrix(0,nlam,p)

  
  if(standardize ==TRUE){
    X.means = apply(X, 2, mean)
    X.sd = apply(X, 2, sd)*sqrt((n-1)/n)
    # remove mean and divided by sd for each column
    Xs = t((t(X) - X.means)/X.sd)
    y.means = mean(y)
    y.sd = sd(y)*sqrt((n-1)/n)
    ys = (y - y.means)/y.sd
  }
  

  # Initialize coef vector b and residual vector r
  
  
  b = rep(0,p)
  r = ys
  # Triple nested loop
  for(m in 1:nlam){
    lam = (2*n*lam.seq[m])/y.sd # assign lambda value
    for(step in 1:maxit){
      for(j in 1:p){
        r = r + (Xs[,j]*b[j])
        b[j] = one_step_lasso(r, Xs[, j], lam)
        r = r - Xs[, j] * b[j]
        }
    }
  B[m, ] = b
}
  
  if(standardize==TRUE){
# scale back the coefficients and update the intercepts B[, 1]
    b_0=c()
    for (i in 1:nlam){
      b_0[i] = y.means - sum(B[i,]*X.means/X.sd)*y.sd
      B[i,]=(y.sd)*B[i,]/(X.sd)
    }
    B = cbind(matrix(b_0,nlam),B)
}

  return(t(B))
}

```

## lasso output in R
```{r}
lasso.fit = glmnet(X, y, alpha = 1, lambda = lam.seq, standardize=TRUE)
coef(lasso.fit)

```


## mylasso output
```{r}
myout = MyLasso(X, y, lam.seq, maxit = 50, standardize=TRUE)
rownames(myout) = c("Intercept", colnames(X))
myout
```


## the difference between mylasso and Rlasso
```{r}
max(abs(coef(lasso.fit)-myout))
```

```{r}

```


```{r}

```


```{r}

```

## Discussion
According to the results above, my lasso and the lasso function in R still have small difference with each other. The reason why the difference occured I guess is because the scale back method for coefficients are not the same. There is some improvement needed to be done with the scale method. 


```{r}

```

